### 2016-06-18 paper/numerical_experiments.tex
more paper edits

Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. Each linear Langrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[h!]
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering    
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \label{fig:baseRef0}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI. In the first elemental decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point. Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region. After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point.

Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}. In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

%------------------------------------------------------------%
\subsubsection{Interaction of Observations and QoI} \label{sec:qoivdata}
%------------------------------------------------------------%
%
lalala
%bigger steps in 3D problem because qoi region bigger?
%usually says to refine in qoi region...but what if qoi region whole domain?
%
\subsection{Constant vs Field Parameters}
%
\subsubsection{Problem Setup}
%
\subsubsection{Results}
%
\subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
%
\subsubsection{Results}
%
We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model. This reaction term is large enough that the Newton solver will not converge with a zero initial guess. We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value). From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
%
\subsubsection{Computational Complexity}
%
We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}. For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.

>>>>

Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. Each linear Langrange basis function's contribution is plotted at its nonzero node.
%
\begin{figure}[h!]
\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering    
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \label{fig:baseRef0}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI. In the first decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point. Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region. After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point.

Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}. In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.\red{does this even have enough points to warrant a graph? or would a table be better?}}
\label{fig:baseErr}
\end{figure}
%

%------------------------------------------------------------%
\subsubsection{Interaction of Observations and QoI} \label{sec:qoivdata}
%------------------------------------------------------------%
%
The error estimate decomposition (\ref{eq:basisblame}) suggests the use of the high-fidelity model in areas of the domain that are important to the interaction of the observations and QoI; the interaction of these two can be complex, and the areas suggested for refinement may be nonintuitive. To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of data points, and for three nested sets of data points given the same QoI region. For the sake of illustration, we make two refinement iterations for each combination of observations and QoI region, regardless of the magnitude of the relative error estimate. However, it was noticed that the number of iterations needed to achieve a given tolerance increased as the QoI region increased, but did not consistently increase or decrease with the number of data points.

The error decomposition for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations is shown in Figure \ref{fig:qoiStudy}. The bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are choesn, so the proportion of additional refined elements in each iteration is slightly larger. Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/setup_5_3.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/setup_7_3.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/setup_3_3.png}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_0.png}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_1.png}
    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_2.png}
    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
    \label{subfig:obsMFlast}
  \end{subfigure}
  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
  \label{fig:qoiStudy}
\end{figure}

The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in Figure \ref{fig:dataStudy}. Again, the bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are choesn, so the proportion of additional refined elements in each iteration is slightly larger. Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region. However, as more data points are added, it becomes no longer necessarily true that refinement becomes less important around data points as their distance from the QoI region increases. The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between.

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/setup_3_10.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/setup_3_5.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/setup_3_3.png}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup2}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_0.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_0.png}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF2}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_1.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_1.png}
    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.20\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_2.png}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_2.png}
    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
    \label{subfig:obsMFlast2}
  \end{subfigure}
  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF2}-\subref{subfig:obsMFlast2}), given the same QoI region (purple box in (\subref{subfig:obsSetup2})) and varying observations (teal points in (\subref{subfig:obsSetup2})).}
  \label{fig:dataStudy}
\end{figure}

%
\subsection{Constant vs Field Parameters}
%
\subsubsection{Problem Setup}
%
\subsubsection{Results}
%
%bigger steps in 3D problem because qoi region bigger?
\subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
%
\subsubsection{Results}
%
We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model. This reaction term is large enough that the Newton solver will not converge with a zero initial guess. We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value). From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
%
\subsubsection{Computational Complexity}
%
We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}. For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.
